\section*{Experience}
\hrule
\vspace{0.3cm}
\subsection*{\small {Vice President, Goldman Sachs \hfill Dec 2019 - present}}
\begin{itemize}[label=\textperiodcentered,labelindent=0pt,itemindent=1em,leftmargin=0.3cm,itemsep=0pt]
    \begin{itemize}[label=\textperiodcentered,itemindent=1em,leftmargin=0.3cm,itemsep=0pt]
        \item \textbf{SecDB 2.0 - Foundation-DB based Distributed Key-val store}
            \begin{itemize}
                \item {Part of core team involved in rewrite of a Distributed key-val store which forms the backbone of all trading and risk activities at GS}
                \item {Led the effort to evaluate various available open source alternatives eg: CouchDB, RocksDB, FDB etc to replace the custom storage engine}
                \item Developed an in-house layer on top of the key-value store to support SQL-like queries and contributed patches back to Foundation-DB for the existing layers.
                \item Performed in-depth cost and performance analysis for optimum cluster setup which increased the read/write thoughput for the store by ~45% and brought down cost by 23%
                \item Presented modeling of SecDb on FoundationDb in KubeCon'19, San Diego. Currently working on it.  
            \end{itemize}        
\end{itemize}
\subsection*{\small{Associate Software Engineer, Goldman Sachs \hfill Nov 2015 - Dec 2019}}
\begin{itemize}[label=\textperiodcentered,labelindent=0pt,itemindent=1em,leftmargin=0.3cm,itemsep=0pt]
    \begin{itemize}[label=\textperiodcentered,itemindent=1em,leftmargin=0.3cm,itemsep=0pt]
        \item \textbf{Remote File System for Bazel}
            \begin{itemize}
                \item {Authored multiple design proposals aimed at improving build infra for a monorepo at GS.}
                \item {Added a Remote file system module for Bazel, an Open source build system developed at Google. This is currently in review for acceptance into the open source repository}
                \item Improved Build performance for a monorepo of size ~4.5 Gbs by a magnitude of 60\% reduction in CI build times
                \item Developed additional tooling around Bazel to be used internally for providing a fine-grained view of a build both as a web service and integration into IDE. 
                \item Led multiple training sessions to familiarize current developers with the new build system and insight into how builds can be optimized
            \end{itemize}
            
        \item \textbf{Data Quality Framework}
            \begin{itemize}
                \item {Co-authored a research paper detailing how Association Rule mining can be used to analyze Data quality issues in a very large dataset}
                \item {The framework improved the efficiency of a mission critical system which sends out reports to UK and US financial regulators, where the punitive damages of missing deadlines is both financial and reputational.
                \item Eliminated human intervention in sanity checking of data by automating discovery of rules on historical data  and generating alerts and action items when tolerance is breached.}
            \end{itemize}
        
        \item \textbf{Portfolio Manager}
            \begin{itemize}
                \item {Led the development of a application for providing access to historical trades to be used by traders from an entire GS business vertical.}
                \item {Trend analysis and Replay of a trade through it's complete lifecycle were provided as niche features leading to wider acceptance of the product across multiple business lines. }
            \end{itemize}
    \end{itemize}
    
\end{itemize}
\subsection*{\small{Software Developer, Royal Bank of Scotland \hfill Jun 2014 - Nov 2015}}
\begin{itemize}[label=\textperiodcentered,labelindent=0pt,itemindent=1em,leftmargin=0.3cm,itemsep=0pt]
    \begin{itemize}
        \item \textbf{Derivatives Settlement Platform}
            \begin{itemize}
                \item {Automated reconciliation of large financial datasets using Spark , based on multiple criterion, providing end users a seamless replacement for custom excel macros and other scripts.}
                \item {Provided a visually rich UI to end users to ease adoption of the product and maintained extensibility by catering to multiple sources and sinks of data}
            \end{itemize}
    \end{itemize}
\end{itemize}
\subsection*{\small{Summer Intern, Royal Bank of Scotland \hfill May 2013 - Jul 2013}}

